---
title: "EDA - 01"
subtitle: "Counting Rows & # Clients"
output: html_notebook
---

```{r}
library(dplyr)
```

# Conteos de Filas y de Clientes {.tabset}

## base1_train
```{r}
base1_train<-readRDS("data/Base1_train.rds")
head(base1_train)
```
- **Número de filas:** `r format(nrow(base1_train), nsmall=1, big.mark=",")`

- **Número de Clientes:** `r format(length(unique(base1_train$COD_CLIENTE)), nsmall=1, big.mark=",")`

## base2
```{r}
base2<-readRDS("data/Base2.rds")
head(base2)
```

- **Número de filas:** `r format(nrow(base2), nsmall=1, big.mark=",")`

- **Número de Clientes:** `r format(length(unique(base2$COD_CLIENTE)), nsmall=1, big.mark=",")`


## base3
```{r}
base3<-readRDS("data/Base3.rds")
head(base3)
```

- **Número de filas:** `r format(nrow(base3), nsmall=1, big.mark=",")`

- **Número de Clientes:** `r format(length(unique(base3$COD_CLIENTE)), nsmall=1, big.mark=",")`


## base4
```{r}
base4<-readRDS("data/Base4.rds")
head(base4)
```

- **Número de filas:** `r format(nrow(base4), nsmall=1, big.mark=",")`

- **Número de Clientes:** `r format(length(unique(base4$COD_CLIENTE)), nsmall=1, big.mark=",")`


## base5
```{r}
base5<-readRDS("data/Base5.rds")
head(base5)
```

- **Número de filas:** `r format(nrow(base5), nsmall=1, big.mark=",")`

- **Número de Clientes:** `r format(length(unique(base5$COD_CLIENTE)), nsmall=1, big.mark=",")`
